Deep Probabilistic Models for Camera Geo-Calibration

### 2018-12-06 dissertation.tex
minor change

I would like to take this opportunity to give my thanks to several
individuals who helped me through the path:  Jinze Liu, who
first got me enrolled to the graduate school; 
Qiang Ye, Judy Goldsmith, and Andrew Klapper, for intriguing
my desire for higher-level knowledge. A huge appreciation to the
other members of my advisory committee, Ruigang Yang and Ramakanth
Kavuluru, for their invaluable feedback through my defense.

>>>>

I would like to take this opportunity to give my thanks to several
individuals who helped me through the path:  Jinze Liu, who
first got me enrolled to the graduate school; 
Qiang Ye, Judy Goldsmith, and Andrew Klapper, for intriguing
my desire for higher-level knowledge. A huge appreciation to 
other members of my advisory committee, Ruigang Yang and Ramakanth
Kavuluru, for their invaluable feedback during my defense.
